\cvsection{Experience}

\begin{cventries}

  \cventry
  {Development Engineer: \textbf{Cloud Monitoring Management}}
  {Fujitsu Technology Solutions Sp. z o.o.}
  {Łódź, Poland}
  {02.2015 - now}
  {
    \begin{cvitems}
      \item[]{
        \textbf{Technical environment}:
        \begin{description}
            \item[Languages] Java, JavaScript, Python2, Python3, YML
            \item[Frameworks/Libraries] NodeJS, Ansible, ORM (Hibernate, Alembic, SQLAlchemy), Crowbar, Chef, Elastic Stack, Tox
            \item[OS] Ubuntu, CentOS, Suse
            \item[Management] CodeBeamer
            \item[QA] Gerrit, Jenkins, BugZilla, OpenStack CI
            \item[Tools] VIM, Pycharm, IntelliJ, RubyMine, VirtualBox, Docker, Devstack
            \item[CVS] \faGithub\acvHeaderIconSep Github, \faGitlab\acvHeaderIconSep Gitlab
        \end{description}
      }
      \item{Initial author of the open source monasca-log-api project
              \href{https://github.com/openstack/monasca-log-api}{\textbf{[\faGithubSquare\acvHeaderIconSep link]}},
          Python implementation, also a contributor to the Java implementation
          of the same project. Projects aims to be a REST-ful
          API receiving logs from agents deployed on target machines to collect them
      }
      \item{Initial author of the open source monasca-kibana-plugin
          project \href{https://github.com/openstack/monasca-kibana-plugin}{\textbf{[\faGithubSquare\acvHeaderIconSep link]}},
          plugin bringing multitenancy of OpenStack to Kibana
      }
      \item{Initial author of the open source keystone-v3-client project
          \href{https://github.com/FujitsuEnablingSoftwareTechnologyGmbH/keystone-v3-client}{\textbf{[\faGithubSquare\acvHeaderIconSep link]}}, keystone binding in NodeJS.
      }
      \item{Author of PostgreSQL support for
          \href{https://github.com/openstack/monasca-api}{\textbf{[\faGithubSquare\acvHeaderIconSep link]}} \textbf{Devstack} plugin}
      \item{Author of major part of
          \href{https://github.com/openstack/monasca-log-api}{\textbf{[\faGithubSquare\acvHeaderIconSep link]}} \textbf{Devstack} plugin}
      \item{Author of several CI adjustments for monasca projects, includes: \textbf{tox}, \textbf{gates setup}}
      \item{Responsible for developing, extending and contributing to several Ansible role}
      \item{Core-Reviewer at OpenStack’s Gerrit for monasca-* projects,
          designed to monitor cloud environment. Status of contribution can be tracked
          \href{http://stackalytics.com/?user_id=kornicameister&release=all&project_type=all&metric=person-day}{\textbf{here}}}
      \item{Active participant during monasca community meetings}
      \item{Monitoring OpenStack}
      \item{Experience in ELK Stack (Elastic Stack)}
    \end{cvitems}
  }

  \cventry
  {Development Engineer: \textbf{OpenService Catalog Manager}}
  {Fujitsu Technology Solutions Sp. z o.o.}
  {Łódź, Poland}
  {01.2015 - 02.2015}
  {
    \begin{cvitems}
       \item[]{
            \textbf{Technical environment}:
            \begin{description}
                \item[Languages] Java, JavaScript, CSS
                \item[Frameworks, Libraries] RichFaces, JSF, Hibernate
                \item[OS] Windows
                \item[Management] CodeBeamer
                \item[QA] BugZilla
                \item[Tools] IntelliJ IDEA, Eclipse
                \item[CSV] \faGitlab\acvHeaderIconSep Gitlab
            \end{description}
       }
       \item{Primarily I have been working with porting an application
             to newer Glassfish (3.x), both
             in server side and client side}
       \item{Responsible for removing all incompatibilities in codebase that
             were a result of migration to newer Glassfish}
    \end{cvitems}
  }

  \cventry
  {Java, JavaScript developer}
  {Transition Technologies Solutions S.A.}
  {Łódź, Poland}
  {02.2013 - 12.2014}
  {
      \begin{cvitems}
        \item{Primarily working with Windchill customization/extensions on 2 different projects.
            One of them was developed for \textbf{Airbus Helicopters} company, focused on
            adding new functionalities according to client specification.
            Actively participated ind development of migration tool to allow \textbf{Airbus Helicopters}
            upload data from their legacy system through JMS queue (Tibco). \
            Customizing Windchill for \textbf{Scania} was short experience. Assignment were circling
            around development of new features, mostly frontend of Windchill.
        }
        \item{Worked as Java/JavaScript developer at project meant to support field technicians.
            Product was build in client-server architecture, having Windchill in the backend and
            web application, based on Angular as a frontend. Being member of this team meant
            working both with JavaScript and Java code.
        }
        \item{Preparing JavaScript trainings (internal, external)}
        \item{Assisting on recruitment of new employees}
        \item{Internship leader}
      \end{cvitems}
  }

  \cventry
  {Intern}
  {Transition Technologies Solutions S.A.}
  {Łódź, Poland}
  {06.2012-09.2012}
  {
      \begin{cvitems}
          \item{Creating a web application supporting life cycle management with ExtJS}
      \end{cvitems}
  }

\end{cventries}
